Parenting observation lexical diversity

### 2017-07-07 parenting_obs_lexdiv.Rmd
add analyses for prereg

```{r}
data <- read.csv("data.csv", header =TRUE)
dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("joint_attention/conditions.csv")

@@

```{r}
d <- left_join(data, conditions)%>%
  left_join(dem)%>%
  transmute(SID=SID, 
            types = Type.count, 
            tokens = Token.count, 
            lexdiv = Lexical.diversity, 
            condition= Condition, 
            video = Video, 
            age = age,
            gender = gender,
            parent_ed = parent_ed)%>%
  filter(!is.na(condition))
```

@@

>>>>

```{r}
data <- read.csv("data.csv", header =TRUE)
dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData")

@@

```{r}
d <- left_join(data, conditions)%>%
  left_join(dem)%>%
  transmute(sid=SID, 
            types = Type.count, 
            tokens = Token.count, 
            lexdiv = Lexical.diversity, 
            condition= Condition, 
            video = Video, 
            age = age,
            gender = gender,
            parent_ed = parent_ed)%>%
  left_join(ids)%>%
  filter(!is.na(condition))
```

@@

Analyses.

Prepare data.
```{r}
lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         lexdiv = as.numeric(lexdiv),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))
```

Predicting lexical diversity based on experimental condition, PAQ, demographics. 
```{r}
maximal_mod <- lmer(lexdiv ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
                           (1| video), 
                         data = lmer_data)
summary(maximal_mod)
```

Predicting the number of word tokens based on experimental condition, PAQ, demographics.  
```{r}
maximal_mod <- lmer(tokens ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
                           (1| video), 
                         data = lmer_data)
summary(maximal_mod)
```

Predicting the number of word types based on experimental condition, PAQ, demographics.  
```{r}
maximal_mod <- lmer(types ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
                           (1| video), 
                         data = lmer_data)
summary(maximal_mod)
```
